Probabilities of polar aligned disks in binary star systems

### 2024-03-11 src/tex/ms.tex
Fix spelling mistakes

% Title
\title{Probabilites of polar aligned disks in binary star systems}

@@

% Abstract with filler text
\begin{abstract}
    Inclined circumbinary disks settle to coplanar or polar-aligned configurations with respect to the binary host.
    The preferred alignment can be found analytically
    in the case of a massless disk, however disk-star interactions make the general case much more challenging.
    We employ the N-body code REBOUND to investigate the dynamics of these 3-body systems and use monte-carlo methods
    to quantify the probabilities of the various configurations in a given system.
\end{abstract}

@@

The orbital parameters of these planets, and the disks that they form from, are determined from their interaction history with their
host stars. These interactions can be broadly split into two catagories:

@@

Planets form with orbital characteristics given by their progenitor disks \citep[e.g.,][]{childs2021}, so it is sufficient in this work to
discuss disk dynamics only.
Differential precession between adjacent annular regions in a disk cause dissapation, ultimately dampening precession or libration
so that the disk reaches a steady state on its viscous timescale \citep[see also \citet{nixon2011,foucart2013,foucart2014}]{bate2000}. Therefore, it is appropriate to map a disk's
initial interactions with a binary (prograde precession, libration, retrograde precession) to the disk's final configuration
(prograte coplanar, circumpolar, retrograde coplanar, respectively).

>>>>

% Title
\title{Probabilities of polar aligned disks in binary star systems}

@@

% Abstract with filler text
\begin{abstract}
    Inclined circumbinary disks settle to coplanar or polar-aligned configurations with respect to the binary host.
    The preferred alignment can be found analytically
    in the case of a massless disk, however disk-star interactions make the general case much more challenging.
    We employ the N-body code REBOUND to investigate the dynamics of these 3-body systems and use Monte Carlo methods
    to quantify the probabilities of the various configurations in a given system.
\end{abstract}

@@

The orbital parameters of these planets, and the disks that they form from, are determined from their interaction history with their
host stars. These interactions can be broadly split into two categories:

@@

Planets form with orbital characteristics given by their progenitor disks \citep[e.g.,][]{childs2021}, so it is sufficient in this work to
discuss disk dynamics only.
Differential precession between adjacent annular regions in a disk cause dissipation, ultimately dampening precession or libration
so that the disk reaches a steady state on its viscous timescale \citep[see also \citet{nixon2011,foucart2013,foucart2014}]{bate2000}. Therefore, it is appropriate to map a disk's
initial interactions with a binary (prograde precession, libration, retrograde precession) to the disk's final configuration
(prograde coplanar, circumpolar, retrograde coplanar, respectively).
